\documentclass[10pt,letterpaper]{article}
\usepackage{hyperref}
\usepackage{geometry}

\geometry{
  body={6.7in, 8.5in},
  left=1.0in,
  top=1.25in 
}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Make lists without bullets
\renewenvironment{itemize}
{
\begin{list}{}{\setlength{\leftmargin}{1.5em}}
}
{
  \end{list}
}

\begin{document}

{\huge Levent Sagun}

\noindent\rule{6.7in}{0.4pt}

\textbf{ Affiliation:} EPFL \textbf{ DOB:} March 28, 1987 \textbf{ Contact:} leventsagun@gmail.com

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Research Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Probability theory, statistical physics, and their applications on deep learning. \\ Statistical and geometric properties of loss functions in machine learning.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \textbf{2011 - 2017 } Ph.D. in Mathematics, Courant Institute of Mathematical Sciences, New York University \\ 
  \hspace*{2cm} \textit{ Thesis title: }{Explorations on High Dimensional Landscapes: Spin Glasses and Deep Learning} \\
  \hspace*{2cm} \textit{ Academic advisors: }{G\'erard Ben Arous and Yann LeCun}

\item \textbf{2006 - 2011 } B.S. in Mathematics, Bo\u{g}azi\c{c}i University, Istanbul, Turkey \\
    %\textit{-GPA:} 3.92 - rank 1$^{st}$, \\
    %\textit{-Double Major:} Physics - rank 1$^{st}$ \\
    \hspace*{2cm} \textit{ Exchange program: }{Columbia University, New York, Fall 2009} %, \textit{SPA:} 4.04
 
\item \textbf{2001 - 2006 } High School, \.{I}stanbul Lisesi, Istanbul, Turkey%(with High Honors degree)

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \textbf{2018 - 2019 } Postdoctoral Fellow, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland \\ 
\hspace*{2cm} \textit{ Simons Collaboration on Cracking the Glass Problem - Part II}

\item \textbf{2017 - 2018 } Postdoctoral Fellow, \'Ecole Normale Sup\'erieure Paris \& CEA Saclay, France \\ 
\hspace*{2cm} \textit{ Simons Collaboration on Cracking the Glass Problem - Part I}

\item \textbf{2015 - 2016 } Teaching Assistant, Center for Data Science, New York University

\item \textbf{2011 - 2017 } Research \& Teaching Assistant, Department of Mathematics, Courant Institute, NYU
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Industry Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \textbf{2016 - 2017 } Research Intern and Contractor, Facebook AI Research, New York \\ 
\hspace*{2cm} \textit{ Manager: }{L\'eon Bottou}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Stefano Spigler, Mario Geiger, St\'ephane d'Ascoli, Levent Sagun, Giulio Biroli, Matthieu Wyart. A jamming transition from under- to over-parametrization affects loss landscape and generalization. Integration of Deep Learning Theories Workshop at NIPS, 2018.

\item David Lopez-Paz, Levent Sagun. Easing non-convex optimization with neural networks. Workshop Track at ICLR, 2018.

\item Marco Baity-Jesi, Levent Sagun, Mario Geiger, Stefano Spigler, G\'erard Ben Arous, Chiara Cammarota, Yann LeCun, Matthieu Wyart, Giulio Biroli. Comparing Dynamics: Deep Neural Networks versus Glassy Systems. Conference Paper at ICML, 2018.

\item Levent Sagun, Utku Evci, V. U\u{g}ur G\"uney, Yann Dauphin, L\'eon Bottou. Empirical Analysis of the Hessian of Over-Parametrized Neural Networks. Workshop Track at ICLR, 2018.

\item  Levent Sagun, Thomas Trogdon, Yann LeCun. Universal halting times in optimization and machine learning. Optimization Workshop at ICML, 2016; and \textit{Quart. Appl. Math.}, \textbf{76}, \textit{289-301}, 2018.

\item Andrew J. Ballard, Ritankar Das, Stefano Martiniani, Dhagash Mehta, Levent Sagun, Jacob D. Stevenson, David J. Wales. Perspective: Energy Landscapes for Machine Learning. \textit{Phys. Chem. Chem. Phys.}, \textbf{19}, 12585-12603, 2017.

\item Matthew Dunn, Levent Sagun, Hale \c{S}irin, Daniel Chen. Early Predictability of Asylum Court Decisions. ML and the Law, ICAIL Pages 233-236, 2017.

\item Pratik Chaudhari, Anna Choromanska, Stefano Soatto, Yann LeCun, Carlo Baldassi, Christian Borgs, Jennifer Chayes, Levent Sagun, Riccardo Zecchina. Entropy-SGD: Biasing Gradient Descent Into Wide Valleys. Conference Track at ICLR, 2017.

% \item  Levent Sagun, Thomas Trogdon, Yann LeCun. Universality in halting time and its applications in optimization. ICML Optimization Workshop Spotlight Poster Session, 2016.

\item  Levent Sagun, U\u{g}ur G\"uney, G\'erard Ben Arous, Yann LeCun. Explorations on high dimensional landscapes. Workshop Track at ICLR, 2015.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Preprints}
\begin{itemize}

\item Mario Geiger, Stefano Spigler, St\'ephane d'Ascoli, Levent Sagun, Marco Baity-Jesi, Giulio Biroli, Matthieu Wyart. The jamming transition as a paradigm to understand the loss landscape of deep neural networks. Preprint, available at arXiv:1809.09349, 2018.

\item Matthew Dunn, Levent Sagun, Mike Higgins, U\u{g}ur G\"uney, Volkan Cirik, Kyunghyun Cho. SearchQA: A New Q\&A Dataset Augmented with Context from a Search Engine. Preprint, available at arXiv:1704.05179, 2017.

\item Levent Sagun, L\'eon Bottou, Yann LeCun. Eigenvalues of the Hessian in Deep Learning: Singularity and Beyond. Preprint, available at arXiv:1611.07476, 2017.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Reviewer duties}
\begin{itemize}
    \item ICLR, JMLR,  COLT, NIPS, TPAMI, SIAM Journal, Cambridge University Press
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Talks and Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item An empirical look at the loss landscape: shape, dynamics, and loose ends, Statistical Physics and Machine Learning back together, Institut d'\'Etudes Scientifiques de Carg\`ese, Corsica, August 2018 \\
Over-parametrization in Deep Learning, Institut f\"ur Theoretische Physik, Heidelberg, July 2018 \\
Easing non-convex optimization with neural networks, ICLR 2018 Poster, May 2018 \\
Empirical Analysis of the Hessian of Over-Parametrized Neural Networks, ICLR 2018 Poster, May 2018 \\
Shape and Dynamics of the Loss Landscape, CILVR Lab Meetings, NYU, New York, April 2018 \\
Shape and Dynamics of the Loss Landscape, High-Dimensional Dynamics Workshop, New York, April 2018 \\
Comparing Dynamics: Deep Neural Networks versus Glassy Systems, Mathematics, Information and Computation Seminar, NYU, New York, March 2018 \\ 
Over-parametrization in Deep Learning, Invited Visit at Google Brain, Zurich, January 2018 \\ 
Over-parametrization in Deep Learning, T\'el\'ecom ParisTech, Paris, November 2017 \\ 
Over-parametrization in Deep Learning, Universit\'e Paris-Sud, Paris, November 2017 \\ 
Over-parametrization in Deep Learning, Facebook AI Research, Paris, October 2017 \\ 
Over-parametrization in Deep Learning, ENS, Paris, October 2017 \\ 
The Role of Over-Parametrization in Optimization, Nonlinear and Stochastic Optimization at SIAM Conference on Optimization, Vancouver, May 2017 \\ 
Singularity of the Hessian in deep learning, CILVR Lab Meetings, NYU, New York, November 2016 \\ 
Universality in Halting Time, Spotlight talk at Optimization Workshop, ICML, New York, June 2016 \\ 
Universality in Halting Time and Optimization, CILVR Lab Meetings, NYU, New York, April 2016 \\ 
Explorations on High Dimensional Landscapes, Spotlight presentation, MLSS Kyoto, September 2015 \\ 
Explorations on High Dimensional Landscapes, Poster presentation, DLSS, U. of Montreal, August 2015 \\ 
Explorations on High Dimensional Landscapes, Poster presentation, ICLR, San Diego, May 2015 \\ 
Optimization in High Dimensional Landscapes, ML Seminar, Bo\u{g}azi\c{c}i University, January 2015 \\ 
High Dimensional Landscapes: Spin Glasses and Deep Learning, ML Seminar, NYU, September 2014 \\ 
Critical Points in High Dimensional Landscapes, NCAP Presentations by Participants, U of T, August 2014 \\ 
An Introduction to Longest Increasing Subsequences, Bo\u{g}azi\c{c}i University, June 2011 \\ 
Insight into Theory of Large Deviations, Department of Mathematics, Bo\u{g}azi\c{c}i University, May 2010 \\ 
Conjugate Gradient Method, Student Seminars in Mathematics and Physics, Bo\u{g}azi\c{c}i University, April 2010
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Educational Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Statistical Physics and Machine Learning back together, Institut d'\'Etudes Scientifiques de Carg\`ese, Corsica, August 2018 \\
Deep Learning and Statistical Physics, Beg Rohu Summer School, June 2018 \\
Machine Learning Summer School, University of Kyoto, September 2015 \\ 
Deep Learning Summer School, University of Montreal, August 2015 \\ 
% International Conference on Learning Representations, San Diego, May 2015 \\ 
CIFAR Neural Computation \& Adaptive Perception Summer School, University of Toronto, August 2014 \\ 
Workshop on Stochastic Gradient Methods, IPAM, February 2014 \\ 
St. Petersburg School in Probability and Statistical Physics, Chebyshev Laboratory, June 2012 \\ 
% Workshop on Random Media: Homogenization and Beyond, IPAM, January 2011 \\ 
Minicourse on Compressed Sensing by Emmanuel Cand\`{e}s, University of Cambridge, March 2011 \\ 
Summer School on Complex Systems, Institute for Theoretical and Applied Physics, Summer 2010 \\ 
Summer School on Computational Solution of Inverse Problems, Helsinki University, Summer 2010 \\ 
Summer School on Dynamical Systems and Their Applications, Utrecht University, Summer 2009 \\ 
Independent Study on Dynamical Systems, Bo\u{g}azi\c{c}i University, Summer 2009 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Recitation leader, Statistical and Mathematical Methods, NYU - Center for Data Science, Fall 2016 \\ 
Recitation leader, Theory of Probability, Courant Institute, Fall 2016 \\ 
Recitation leader, Machine Learning, NYU - Center for Data Science, Fall 2015 \\ 
Recitation leader, Statistical and Mathematical Methods, NYU - Center for Data Science, Fall 2015 \\ 
Recitation leader, Probability and Statistics, Courant Institute, Spring 2015 \\ 
Recitation leader, Theory of Probability, Courant Institute, Fall 2014 \\ 
Teaching assistant, Introduction to Mathematical Analysis II, Courant Institute, Spring 2014 \\ 
Instructor for the Written Exam Workshop, Courant Institute, Fall 2013 \\ 
Teaching Assistant for Statistics and Probability, Bo\u{g}azi\c{c}i University, 2009-2010
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Honors, Awards \& Fellowships}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item MacCracken Fellowship, New York University, 2011-2016 \\
Dora Aksoy Award, Department of Mathematics, Bo\u{g}azi\c{c}i University, 2011 \\ 
Hilmi Tolun Award, Faculty of Arts and Sciences, Bo\u{g}azi\c{c}i University, 2011 \\ 
% T\"{U}B\.{I}TAK Scholarship, 2006 - 2011 \\
% Alize-Bar\i\c{s} Tansever Exchange Student Scholarship, Bo\u{g}azi\c{c}i University, 2009
%\item Placed 374$^{th}$ in the nationwide university entrance exam among 1,510,000 high school students, 2006 \\ 
% `Final Award' in the high school project competition organized by the Turkish Ministry of Education, 2005 \\ 
Honorable Mention, 9$^{th}$ National Mathematical Olympiads, Akdeniz University, Antalya, Turkey, 2004 \\ 
Silver Medal, 5$^{th}$ National Mathematical Olympiads for Junior High School Students, T\"{U}B\.{I}TAK, 2001
\end{itemize}

\section*{References}

\subsection*{Research}

\begin{itemize}

\item \textbf{G\'erard Ben Arous} - \url{benarous@cims.nyu.edu} \\
Professor of Mathematics, Courant Institute of Mathematical Sciences, NYU \\
Associate Provost for the Quantitative Disciplines, Global Network Professor of Mathematics, NYU Shanghai \\
\textit{Relationship:} PhD thesis advisor

\item \textbf{Giulio Biroli} - \url{giulio.biroli@ens.fr} \\
Professor of Theoretical Physics \\
Laboratoire de Physique Statistique, \'Ecole Normale Sup\'erieure, PSL Research University, Paris, France \\
\textit{Relationship:} Postdoc advisor

\item \textbf{L\'eon Bottou} - \url{leonb@fb.com} \\
Research Lead, Facebook AI Research, New York \\
Visiting Research Professor, Computer Science Department, NYU \\
\textit{Relationship:} Manager at FAIR and PhD thesis co-advisor

\end{itemize}

\subsection*{Teaching}

\begin{itemize}

\item \textbf{Carlos Fernandez-Granda} - \url{cfgranda@cims.nyu.edu} \\
Assistant Professor of Mathematics and Data Science \\
Courant Institute of Mathematical Science and Center for Data Science NYU \\
\textit{Relationship:} I have been his teaching assistant at the Center for Data Science

\end{itemize}

% \subsubsection*{Contact}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today
  \end{footnotesize}
\end{center}

\end{document}
